\section{Mar 30 Review Questions}
\begin{QandA}
   \item How do Byzantine failures break a previous algorithm we've looked at (you pick another algorithm and compare)?
         \begin{answered}
         For example, server with Byzantine failure can make the fake vote to other servers during the leader election phase of the RAFT.
         Thus, there can be multiple leaders to send out commit request, which may lead to serious consensus problem. Another
         example is chord. Byzantine failure can make a server mistakenly states that the key is not located in it or the server
         can give wrong information in the finger table that breaks $O(\log N)$ lookup guarantee.
         \end{answered}

   \item  What assumptions does Coda make about system behavior that allow it to be effective?
         \begin{answered}
         Coda assumes that at certain times, a client may be temporarily unable to communicate with some or all
         of the servers and thus, coda uses to cache to allow users to read and write files even they are disconnected.
         In addition, Coda assumes access and sharing patterns typical of academic and research environment. In other words,
         Coda is not built for applications that need highly concurrent, fine granularity data access. This assumption
         makes Coda to adopt Optimistic Replica Control, which provides high availability by permitting reads and writes 
         everywhere. Since the concurrent access is low (i.e., the low degree of write-sharing typical of Unix), modification
         conflicts for one file by many users may be low and thus, the chance that Coda has to notify the users to resolve
         conflicts is small, which does not impact usability much. 
		 Furthermore, Coda assumes clients can communicate with the servers over a high bandwidth network. As the result, the 
		 process of reconnecting and propagting changes can be done about a minute. Also, the small amount of data makes
		 the storage requirement on clients low as well (e.g., 100MB), which helps with the fast propagation after the reconnection.
         \end{answered}
\end{QandA}




