\section{April 06 Review Questions}
\begin{QandA}
   \item  What does Petal sacrifice in order to achieve its high consistency and low latency? (Hint: Look at the performance test setup.)
         \begin{answered}
		 Petal relies on the ATM hardware to achieve its high consistency and low latency. However, due to the characterstics of ATM hardware,
		 which is used for voice and video, Petal is vlunerable to network partition. If the data is large, there might be network congestion,
		 which fails the high consistency and low latency provided by Petal.
         \end{answered}

   \item  Frangipani was written about 20 years ago. How would you expect the design decisions in this system to hold up to today's needs?
         \begin{answered}
		 Frangipani uses multiple-reader/single-writer locks to coordinate the access to the virtual disk and to keep the buffer caches
		 coherent across the multiple servers. However, when compared with modern system like GFS, the lock service might be the bottleneck
		 for the system performance because it does not allow the concurrent write, which is a critical factor for modern system
		 high performance (i.e., high throughput).		 
         \end{answered}
   \item How does the Google File System's relaxed consistency model benefit the system design?
         \begin{answered}
         GFS's relaxed consistency model greatly simplfies the file system design without imposing large burden on the application.
         In addition, relaxed consistency model allows each machine forwards the data to the ``closest" machine in the network topology
         that has not received it, which avoids the network bottlenecks and high-latency links as much as possible. Furthermore, relaxed
         consistency model decouples the data flow from the control flow, which improve performance by scheduling the expensive data 
         flow based on the network topology regardless of which chunkserver is the primary. Lastly, a strict consistency model
         may bring complex implementation of the file system. However, with a few simple techniques (e.g., relying on appends rather than overwrites, checkpointing, and writing self-validating, self-identifying records) on applications, we can much reduce implementation complexity.
         \end{answered}
   \item How is BigTable able to avoid having the master be a bottleneck?
         \begin{answered}
         Client library caches tablet locations, which avoids much traffic to visit master querying the tablet locations.
         \end{answered}
\end{QandA}




