\section{April 13 Review Questions}
\begin{QandA}
   \item  In Dynamo, Table 1 lists several approaches that the designers used to address their challenges and provides an advantage for each. Pick two techniques and list a disadvantage for each.
         \begin{answered}
         Consistent hashing has its own two problems: 1. random position assignment of each node on the ring leads to non-uniform data and load
         distribution; 2. the algorithm is oblivious to the heterogeneity in the performance of nodes. Dynamo tends to fix this problem by introducing
         ``virtual nodes". However, by using virtual nodes, the system complexity increases as virtual nodes need to maintain extra information
         about whether they are in the same physical node. In addition, when we add nodes into the ring, we need to assign the tokens such that
         the load can be distributed uniformly, which further increases the system complexity. Furthermore, the gossip-based membership protocol
         and failure detection adds extra burden to each individual node and it can hardly scale to more 1000 servers.
         \end{answered}

   \item  How is RAMCloud's design affected by keeping all data in DRAM?
         \begin{answered}
         RAMCloud requires all data in DRAM. Due to this requirement, RAMCloud requires all the DRAM has an auxiliary power source, which ensures
         that buffers can be written to stable storage after a power failure. In addition, since all data has to be in DRAM, during the recovery,
         all the data has to be recovered into DRAM instead of on the SSD or hard disk, which leads to the unwanted disk I/O and the recovery scheme
         complexity.
         \end{answered}
\end{QandA}




