% To compile, run the following command:
%   latexmk -pdf hw_template.tex 
%
% To edit, you can use your favorite text editor or LaTeX editors such as:
%   Texmaker and TeXworks.
%
% To setup your own TeX system, you can install TeX Live. See:
%   https://www.tug.org/texlive/

\documentclass[letterpaper,12pt]{article}
\pagestyle{myheadings}

\include{macros}

\begin{document}
	
\title{Solution to Algorithm Illuminated (Part 4)}
\date{\today}
\author{Zeyuan Hu}
\maketitle
	
\begin{abstract}
This document contains my own solution to \cite{Roughgarden2020}. Mistakes are corrected using \red{red}.
\end{abstract}

\tableofcontents

\section{Chapter 19}

\begin{problem}{19.1}
\end{problem}

b) and c)s

\begin{problem}{19.2}
\end{problem}

\begin{itemize}
	\item a) is false because by Clayley's formula, there are $n^{n-2}$ different spanning trees for a complete graph with $n$ vertices. Thus, the number of spanning tree of a graph is not polynomal in the number $n$ of vertices and the number $m$ of edges. Further, the MST problem is computationally tractable because there exists polynomial algorithms to solve the problem.
	\item b) is false because there are at most $n^{n-2}$ possibilities for the total cost of a spanning tree of a graph
	\item c) is true.
	\item d) is false. Similar to a), the exponential number of travling salesman tours does not necessarily indicate that the TSP is computationally intractable.
\end{itemize}

\begin{problem}{19.3}
\end{problem}

b)

\begin{problem}{19.4}
\end{problem}

a).  c) is false because if an input to an NP-hard problem is well-structured, the problem can be solved in polynomial time.

\begin{problem}{19.5}
\end{problem}

e). b) is false because intuitively, $A$ can be reduced to another problem $C$. If $C$ is polynomial-time solvable, then $A$ is polynomial-time solvable. a) is false because it could be the case that $A$ is polynomial-time solvable because it is reduced to a polynomial-time solvable problem $C$, which is not $B$. As a result, the fact that $A$ is polynomial-time solvable  cannot be used to justify $B$ is polynomial-time solvable.




	
	
	
	
\clearpage
\bibliographystyle{alpha}
\bibliography{papers}
\end{document}